\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/figures.tex

\newcommand{\FigOverview}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{Dark Decoy Overview}\,---\, %
    }
    \label{fig:overview}
\end{figure*}
}

\newcommand{\FigHighLevel}{
\begin{figure}[t]
    \centering
    \vspace{-0.5in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{Overview}---%
      When deployed at an ISP, \scheme observes a mirror of inbound and outbound traffic.
      Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
      address in the ISP's AS, and \scheme communicates with the client as if it were a proxy at that address.
    }
    \label{fig:overview}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[ht]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{Dark Decoys}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
    \label{tab:compare}
\end{table*}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Overview}\,---\, %
    }
    \label{fig:overview}
\end{figure*}
}

\newcommand{\FigHighLevel}{
\begin{figure}[t]
    \centering
    \vspace{-0.5in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{Overview}---%
      When deployed at ISPs, \scheme monitors a passive network tap.
      Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
      address in the ISP's AS, and \scheme injects packets to communicates with the client as if it were a proxy server at that address.
    }
    \label{fig:overview}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[ht]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
    \label{tab:compare}
\end{table*}
}
